\documentclass{article}
\title{Untitled}
\author{Malcolm Ramsay}
\date{2015-2-23}
\begin{document}
\maketitle

At meny levels of chemistry you are told that there are three stte s of matter, solid, liquid and gas. In Physics you mightlearn about the more exotic states of plasma and bose einstein condensate, but you don't have to look past your smartphone so see states outside of those three you learn about. The screen of the phone is made of a glass, quite probably gorilla glass. This is used because of its hardness and imperviousness to scratched, but also because it is flexible, deviations in the structure are not going to lead to cracks, although with enough force it is still going to break. The screen itself is a is a LCD TN panel according to marketing speak, it translates to a liquid crytal display, twisted nematic panel. The nematic phase is found where there are rod like molecules which are roughly ordered in sheets but there is not distinct orientational order\tocheck. Then moving to the camera lens and home button which are covered in sapphire glass, a material even harder than gorilla glass but with many of the same properties. Corning (makers of gorilla glass, and corningware, and lab glass) recently ran an advertising campaign on youtube stating that we are in the glass age. In many ways they are true, the devices that we carry around with us are becoming smaller and smaller and demanyd ever stronger and more scratch resistant materials, even the materials that we have are not strong enough, how often do you see someone with a cracked sceen on their phone. 

Part of the reason that we don't currently have indestructible screens is a lack of understanding of the formation of glassy and crystal phases. We know that there are metallic and molecualr crystls that form, however we have no idea why there is are si\
My project aims to give insight into the formation of glasses and crystals, with particular whmphasis on molecules and the role of shape and concavites in the processes that drive these events. The process of forming a crystal or a glass requires paspanes - a mirror plane combined with a translation and screw axes - which is a rotation ombined with a translation. these symmetery operation have to be combined with all the possible uit cell shapes known as bravais lattices. 

In anuydiscussion of craystals we have to talk about  unit cells, these are the building lbocks of the crystal and we can describve a crystal by it's unit cell, eg \c{NaCl} type crystal or a \ce{zn2s} type crystal.\ce{CsCl}. When descibingh the unit cell one of the parameters thT WE USE IS THE SHAPE, a cubic, orthorhombic or hexagonal unit cell. gthese shapes are decsibed as \tocheck. The second desciptor is how the atoms are arraged with in the unit cell, know as bravis latticels . THe final desciptor of the unit cell is the symmetry operations that make  up, these are rotations ,importper rotations, screw axes, miglide planes that take the position of one atom and from the series of transformations create the position s of all the other atoms in the cell., Together these geometries, bravais lattices and synmetry operations describe the space group of a unit cell. The spacce grtoup is a systematic way of describing the a unit cell. It allows comparison of similar unit cells and makes up the smalles tdesciption of the unit cell. The space gourp and the position of one set of atoms withing the unit cell uis enough to completely recreate the unit cell. There are 219 of these spcae groups, 230 if you include chiral copies. 

Along with the space group of the crystal structure another property of a crystal structure is the proportion of space taken up by the crystal structure, known as the packing fraction. When dealing with crystals a resonable aproximation is to treat all the atoms as hard spheres. This makes calculating the packing fraction a simple task, take the unit cell, place the appropriately sized spheres at all the atom coordinates and calculate the volume of the unit cell occupied by the spheres as a fraction of the total unit cell volume. The packing fraction of the unit cell is related to the energy of the unit cell, with more densely packed structures being favourable. This is one of the ways that we can predict the crystal structure of a molecule, the densest packing is most favourable. The simplest example of this is packing spheres, the simple cubic form gives a packing fraiton of 0.52, the body centered cubic 0.68 and the hexagonal close packed or face centered cubic give the densest packing of 0.74. While it has been taught for a long time that the hexagonal close packed and the face centered cubic structures are the most efficient packing of spheres in 3D space, it was first proposed by kepler in 1611, there has only recently been a rigorous mathemetical proof. Hales has spent the last 20 years working on this problem and with the help of computers to sample all possible configurations has recently completed this proof. So if it took so long to prove the optimal packing of spheres how much harder is it going to be for nonspherical particles. Fortunately there are a ncouple of simplifications that we can make. Firstly while a mathematically rigorous proof is nice, I can quite happily work without one. Secondly 3D is hard, adding the extra dimension adds far more complexity to the problem, 2D is far more manageable (there is a reasonably sized proof of the packing of circles on a plane). The first simplification allows the use of computer programs to search the space of arrangements. There are a number of different algorithms which are based on the idea that there is a multi demensional search landscape through which the particles can move, the height of the landscape determined by the packing fraction, then it is just a case of finding the minimum. This is a common problem in computer science, and one solution is simulated annealing. This is a process very similar to glass formation (see later chapter} where at high 'temperature' the motion of the molecules with in the space is large, then the 'temperature' is slowly reduced. Along with the temperature the motion of the particles is proportional to the depth of the well, the deeper the well the better the solution. Ideally the final configuration will be the closest packed structure but being non-deterministic there is no guarantee. There have been a number of studies just using this first simplification, however there has been much more done in two dimensions.

Most of the work done on packing has been with convex particles where two particles are only able to contact along a single surface. However when treating molecules as a set of spheres connected to each other there are going to be concavities. Concave particles allow multiple points of contact.







\end{document}

